 Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings

### 2020-04-23 paper.Rmd
add quickdraw data

### Case Study 3: QuickDraw images

>>>>

This will be Macosko data

### Case Study 3: How do people draw animals?

In the final case study, we explore a subset of the Google QuickDraw dataset [@quickdraw]. The data are sketches drawn by people of common concepts
like 'airplane' or 'shoe', and corresponding metadata about the humans who
created the sketches, such as country, the word category, whether the sketch
was recognised by Google's neural network, and the number of strokes taken.
We downloaded the metadata and normalised 28 by 28 pixel bitmaps via the `quickdraw` package in R. We sampled 500 images from each of the following  animal categories: "dog", "cat", "octopus", "spider", and "whale" and unravelled the bitmaps into a 784 dimension image vector.
